The Multi-Stencil Framework: A Component-Based Approach to Orchestrate Stencils

### 2017-03-06 ARTICLES/IJPP/articleR1/evaluation.tex
relecture eval

This section first presents the implementation details chosen to evaluate MSF in this paper. Then, the studied use case is presented. Once this context is clear the MSC performance is evaluated as well as both available parallelization techniques, data and task. Finally, the performance model proposed in Section~\ref{sect:perfs}.

@@

The two main implementation choices to take in MSC and its specialized assembly generation concern the technologies used for data and task parallelizations.

@@

For the task parallelism, we have chosen to use OpenMP~\cite{660313} to generate the code of the $Scheduler$ component. OpenMP targets shared-memory platforms only. Although the version 4 of OpenMP has introduced explicit support for dynamic task scheduling, our implementation only requires version 3 whose fork-join model is well suited for the static scheduling introduced in Section~\ref{sect:parallelism}.
The use of dynamic schedulers, such as provided by libgomp\footnote{\url{https://gcc.gnu.org/projects/gomp/}}, StarPU~\cite{Augonnet2011}, or XKaapi~\cite{Gautier:2013:XRS:2510661.2511383},  to directly execute the DAG $\Gamma_{dep}$ will be the subject of future works.

As a result, the MSL compiler generates a hybrid code which uses both SkelGIS and OpenMP.
It also generates empty components where the developer must provide local sequential implementations of the kernels. In our case these kernels are written using SkelGIS API.

@@

%-------------------------------------
\subsection{Compiler evaluation}

Table~\ref{fig:exectime} illustrates the execution time of each step of MSC for the FullSWOF2D example.
This has been computed on a laptop with a dual-core Intel Core i5 1.4~GHz, and 8~GB of DDR3.
While the overall time of 4.6 seconds remains reasonable, one can notice that the computation of the $TSP$ tree is by far the longest step.
As a matter of fact, the complexity of the algorithm for N-shapes removal is $O(n^3)$.
If this complexity is not a problem at the moment and onto this use case it could become one for just-in-time compilation or bigger simulations. The replacement of the static scheduling by a dynamic scheduling using dedicated tools (such as OpenMP 4, StarPU etc.) should solve this in the future.

@@

In this evaluation, we disable task-parallelism to focus on data-parallelism. Two versions of code are compared in this section: first a plain SkelGIS implementation of FullSWOF2D, where synchronizations and fusions are handled manually; second, the automatic synchronizations and fusions handled by MSF over SkelGIS. SkelGIS has already been evaluated in comparison with a native MPI implementation for the FullSWOF2D example~\cite{CPE:CPE3494}. For this reason, this section uses the plain SkelGIS implementation as the reference version. This enables to evaluate both the choices made by MSC as well as the potential overheads of using \llc~\cite{l2c} that is not used in the plain SkelGIS version. The evaluations have been performed on the Curie supercomputer (TGCC, France) described in Table~\ref{tab:TGCC}. Each evaluation has been performed nine times and the median is presented in results.

\begin{table}[!ht]
\begin{center}
 \begin{tabular}{|c|c|}
     & TGCC Curie Thin Nodes\\
     \hline         
    Processor & 2$\times$SandyBridge\\
    & (2.7 GHz)\\
    Cores/node & 16 \\
    RAM/node & 64 GB\\
    RAM/core & 4GB\\
    Compiler [-O3] & gcc 4.9.1\\
    MPI & Bullxmpi\\
 \end{tabular}
 \caption{\label{tab:TGCC}Hardware configuration of TGCC Curie Thin nodes.}
 \end{center}
\end{table}

Figures~\ref{fig:weak1}, \ref{fig:weak2} and~\ref{fig:weak3} respectively show weak scalings for a computation domain of $400 \times 400$ cells by core, $600 \times 600$ cells by core and $800 \times 800$ cells by core from 16 cores to 16.384 cores, as resumed in Table~\ref{tab:weak}.

@@

From these results, one can notice first that performances of MSF are very close to the reference version using plain SKelGIS. This is a very good result which shows first that MSC performs good synchronizations and fusions, and second that overheads introduced by \llc are limited thanks to a good granularity in GA.
However, it seems that a slightly drop of performance happens when the domain size per core increases. This performance decrease is really small though, with a maximum difference between the two versions of 2.83\%.

The only noticeable difference between the two versions are due to \llc which load dynamic libraries at runtime. Because of this particularity, components of \llc are compiled with the \emph{-fpic} compilation flag while the SkelGIS version does not. This flag can have slight positive or negative effect on code performance depending on the situation and might be responsible for the observed difference.

@@

Figure~\ref{fig:strong} shows the number of iteration per second for a 10k$\times$10k global domain size from 16 to 16.384 cores. The total number of time iterations for this benchmark is $1000$. In addition to the reference SkelGIS version, the ideal strong scaling is also illustrated in the figure.

First, one can notice that the strong scaling evaluated for the MSF version is close to the ideal speedup up to 16.384 cores, which is a very good result. Moreover, no overheads are introduced by MSF which shows that automatic synchronizations and automatic fusions are the same one that the one written manually into the plain SkelGIS version. Finally, no overheads are introduced by components of \llc. A small behavior difference can be noticed with $2^9=512$ cores, however this variation is no longer observed with 1024 cores.

@@

In this section, we introduce task parallelism to evaluate the hybrid parallelization offered by MSF. The MSF implementation evaluated in this paper relies on SkelGIS and OpenMP.

@@

\begin{figure}[bh]\begin{center}
  \includegraphics[width=.6\textwidth]{../results/task_scaling/500_200/analytic/times.pdf}
  \caption{Computation vs communication times in the data parallelization technique.}
  \label{fig:limit}
\end{center}\end{figure}

On the other hand, Fig.~\ref{fig:limit} illustrates limitations of data parallelization technique alone. In this figure is represented the execution time (with a logarithmic scale) of FullSWOF2D while increasing the number of cores for a fix domain size of $500 \times 500$ with a total of $200$ time iterations (\ie this is a strong scaling). The speedup of this same benchmark is represented in blue in Fig.~\ref{fig:close}. One can note that the scaling is not as good is the one presented in Fig.~\ref{fig:strong}. 
The main difference between these two benchmarks is the domain size. In the benchmark of Fig.~\ref{fig:strong} the domain size is $10k \times 10k$ which means that using $2^8$ cores, for example, each core has to compute only a $31 \times 31$ sub-domain. On the other hand using $2^8$ cores in Fig.~\ref{fig:close} each core has to compute a $625 \times 625$ sub-domain. Fig.~\ref{fig:limit} shows why the speedup is not as good as the one with a bigger domain size.

@@

All in all, when the number of core used increases, the computation/communication ratio becomes poorer and poorer. As a result, the data parallelism alone fails to provide enough parallelism to leverage the whole machine and other sources of parallelism have to be found. As expected, in  Figure~\ref{fig:close} the speedup bends down from 256 to 2048 cores. The same problem would happened in previous experiment of Fig.~\ref{fig:strong}, however as the domain size is larger, the phenomena appears with much more cores.

@@

In addition to the blue curve, Fig.~\ref{fig:close} shows speedups for the same example ($500 \times 500$ domain with $200$ iterations) but using an hybrid parallelization. Fig.~\ref{fig:close} shows a comparison with 2, 4, 8 and 16 cores per MPI process for task parallelization.

For example, the purple curve shows the parallelization which uses for each data parallelization process (\ie MPI process) 8 additional cores for task parallelization. As a result, for example, when using 2 machines of the TGCC cluster, with a total of 32 cores, 4 cores are used for SkelGIS MPI processes, for data parallelization, and for each one 8 cores are used for task parallelization ($4 \times 8 = 32$). This respect $P = P_{data} \times P_{task}$ presented in Section~\ref{sect:perfs}.
As a result, and as explained in Section~\ref{sect:perfs}, quantities are less divided into sub-domains, that are responsible for communications, and the effect which is observe onto the blue curve is delayed.

@@

First, thin nodes of the TGCC Curie are built with two NUMA nodes each of 8 cores. As a result, when increasing the number of OpenMP cores for task parallelization from 8 to 16 cores, an overhead is introduced by exchanges of data between memories of the two NUMA nodes. This phenomena is illutrated in Fig.~\ref{fig:spread}. In this figure, a different binding strategy is used. A binding strategy is the way the scheduler binds threads onto available cores. The strategy used in Fig.~\ref{fig:spread} is called \emph{spread} (instead of \emph{close} in Figure~\ref{fig:close}). This strategy binds threads on cores in order to spread as much as possible onto resources, which means that the two NUMA nodes are directly used whatever the number of cores used for task parallelism. As a result, and as shown in the figure, using 2, 4 and 8 cores an initial overhead is introduced as the one observed in Fig.~\ref{fig:close}. This shows that the initial overhead with 16 cores is due to NUMA effects.

@@

The second phenomena that happens in Figure~\ref{fig:close} using 16 cores is due to the level of parallelism introduced by the task parallelization technique. Actually, as illustrated in Table~\ref{fig:freq}, only two forks of $TSP$ can take advantage of 16 cores among a total of 18 forks. This phenomena has been mentioned in Section~\ref{sect:perfs} by the variable $F_{task}$ and the fact that it is not always true that $F_{task}=P_{task}$. This explains why using 16 cores is less efficient than using 8 cores, even when the two NUMA nodes are always used as in Fig.~\ref{fig:spread}.

Finally, to validate the performance model introduced in Section~\ref{sect:perfs}, and to understand when the hybrid parallelization becomes more interesting than the data parallelization, Figure~\ref{fig:tth2} represents $T_{COM1}$ and $T_{COM2}+T_{task}$ of Equation~(\ref{eq:hyb}), for the best case, \ie when 8 cores are used in Fig.~\ref{fig:close}.  Figure~\ref{fig:tth2} and Table~\ref{fig:tth} presents results of these measurements. Results perfectly matches Fig.~\ref{fig:close} for 8 cores per MPI process. As a result, the hybrid parallelization becomes better with a total of 512 cores in this case.

@@

\begin{figure}[!h]\begin{center}
  \resizebox{8cm}{!}{\includegraphics{../results/task_scaling/500_200/analytic/tth.pdf}}
  \caption{Execution times (seconds) of $T_{COM1}$ and $T_{COM2} + T_{task}$ for 8 cores for task parallelization. Verification of the Equation~(\ref{eq:hyb}).}
  \label{fig:tth2}
\end{center}\end{figure}

@@

In this section we propose an evaluation of the fusion optimization. Three fusion optimizations have been formally detailed in Section~\ref{sect:fusion}. From the $TSP$ tree computed by MSC it is possible according to specific conditions to merge domain loops of kernels, thus optimizing the use of cache memories.

Figure~\ref{fig:fusion} shows the number of iterations per second as a function of the number of cores with and without fusions. This benchmark is performed on FullSWOF2D onto a $500 \times 500$ domain size with $200$ time iterations, and by using data parallelism alone (without tasks). As explained in Section~\ref{sect:fusion}, the MSF loop fusion happens at a high level. Most of the time such fusions are done naturally by a computer scientist. However, for a numerician who usually writes equations more than numerical codes, an automatic detection of such fusions avoids errors, particularly for a parallel execution. In addition to this, more advanced fusion cases, such as a scatter are more difficult to deduce. In FullSWOF2D a total of  62 fusions are proposed by MSF over a total of 98 computation kernels. Fig.~\ref{fig:fusion} shows that the performance is clearly improved (around 40\%) by these fusions.

@@

Blue curves of Fig.~\ref{fig:fusion1} represent results for data parallelism only with and without fusion. One can note that the best performance, as expected, is reached by the version using fusions. Green curves represent results by using 2 cores per MPI process dedicated for tasks, with and without fusion again. One can note that the best performance is also reached by the version using fusion.

\begin{figure}[!h]\begin{center}
  \includegraphics[width=.6\textwidth]{../results/task_scaling/500_200/withwithout2_close_median.pdf}
  \caption{blabla}
  \label{fig:fusion1}
\end{center}\end{figure}

However, to deeper analyze this results, we propose a second evaluation presented in Fig.~\ref{fig:fusion2}. The blue curves are exactly the same one than in Fig.~\ref{fusion1}. The purple curves, on the other hand, represent results by using 8 cores per MPI process dedicated to tasks, with and without fusion. Interesting results appears in this figure as the hybrid version using fusions is less efficient than the one without fusions. As already explained, this result is due to the fact that fusions reduce the number of tasks from 98 to 36 resulting in a non optimized use of eight cores for task parallelism. By using only 2 cores per MPI process (in Fig.~\ref{fig:fusion1}) the 36 computation kernels were enough to feed the two cores, while it is not for eight.

\begin{figure}[!h]\begin{center}
  \includegraphics[width=.6\textwidth]{../results/task_scaling/500_200/withwithout8_close_median.pdf}
  \caption{blabla}
  \label{fig:fusion2}
\end{center}\end{figure}

As a result, if fusion optimization incurs a too large reduction of the number of tasks to feed dedicated cores, the problem observed for 16 cores in Fig.~\ref{fig:close} happens earlier which reduces obtained performances.

>>>>

This section first presents the implementation details chosen to evaluate MSF in this paper, and the studied use case. Then, the compilation time of MSC is evaluated before analyzing both available parallelization techniques, data and hybrid (data and task). Finally, the impact of fusioning kernel is studied.
\CP{J'ai enlev\'e la ref au mod\`ele de perf car pas trouv\'e  dans les titres de sous-section}
%performance model proposed in Section~\ref{sect:perfs}.

@@

The main choices to take when implementing MSC and its specialized assembly generation concern the technologies used for data and task parallelizations.

@@

For the task parallelism, we have chosen to use OpenMP~\cite{660313} to generate the code of the $Scheduler$ component. OpenMP targets shared-memory platforms only. Although the version 4 of OpenMP has introduced explicit support for dynamic task scheduling, our implementation only requires version 3 whose fork-join model is well suited for the static scheduling introduced in Section~\ref{sect:parallelism}.
The use of dynamic schedulers, such as provided by libgomp\footnote{\url{https://gcc.gnu.org/projects/gomp/}}, StarPU~\cite{Augonnet2011}, or XKaapi~\cite{Gautier:2013:XRS:2510661.2511383},  to directly execute the DAG $\Gamma_{dep}$ is left for future work.

As a result, the MSL compiler generates a hybrid code which uses both SkelGIS and OpenMP.
It also generates components where the developer must provide local sequential implementations of the kernels. In our case these kernels are written using SkelGIS API.

@@

%-------------------------------------
\subsection{Multi-Stencil Compiler evaluation}

Table~\ref{fig:exectime} illustrates the execution time of each step of MSC for the FullSWOF2D example.
This has been computed on a laptop with a dual-core Intel Core i5 1.4~GHz, and 8~GB of DDR3.
MSC has been implemented in Python.
\CP{J'ai ajout\'e la phrase précédente. Est ce correct ? Quelle version de Python ? 2 ou 3 ? Combien de ligne de code ?}
%
While the overall time of 4.6 seconds remains reasonable, one can notice that the computation of the $TSP$ tree is by far the longest step.
As a matter of fact, the complexity of the algorithm for N-shapes removal is $O(n^3)$.
If this complexity is not a problem at the moment and onto this use case it could become one for just-in-time compilation or more complex simulations. The replacement of the static scheduling by a dynamic scheduling using dedicated tools (such as OpenMP 4, StarPU etc.) should solve this in the future.

@@

In this part, we disable task-parallelism to focus on data-parallelism. Two versions of the code are compared in this section: first a plain SkelGIS implementation of FullSWOF2D, where synchronizations and fusions are handled manually; second, the synchronizations and fusions are automatically handled by MSF over SkelGIS. SkelGIS has already been evaluated in comparison with a native MPI implementation for the FullSWOF2D example~\cite{CPE:CPE3494}. For this reason, this section uses the plain SkelGIS implementation as the reference version. This enables to evaluate both the choices made by MSC as well as the potential overheads of using \llc~\cite{l2c} that is not used in the plain SkelGIS version. The evaluations have been performed on the Curie supercomputer (TGCC, France) described in Table~\ref{tab:TGCC}. Each evaluation has been performed nine times and the median is presented in results.

\begin{table}[!ht]
\begin{center}
 \begin{tabular}{|c|c|}
     & TGCC Curie Thin Nodes\\
     \hline         
    Processor & 2$\times$SandyBridge\\
    & (2.7 GHz)\\
    Cores/node & 16 \\
    RAM/node & 64 GB\\
    RAM/core & 4GB\\
    \#Nodes & 5040 \\
    Compiler [-O3] & gcc 4.9.1\\
    MPI & Bullxmpi\\
 \end{tabular}
 \caption{\label{tab:TGCC}Hardware configuration of TGCC Curie Thin nodes.}
 \end{center}
\end{table}

Figures~\ref{fig:weak1}, \ref{fig:weak2} and~\ref{fig:weak3} respectively show weak scalings for a computation domain of $400 \times 400$ cells by core, $600 \times 600$ cells by core and $800 \times 800$ cells by core from 16 cores to 16,384 cores, as summarized in Table~\ref{tab:weak}.

@@

From these results, one can notice first that performances of MSF are very close to the reference version using plain SkelGIS. This is a very good result which shows first that MSC performs good synchronizations and fusions, and second that overheads introduced by \llc are limited thanks to a good component granularity in the Generic Assembly.

However, it seems that a slightly drop of performance happens when the domain size per core increases. This performance decrease is really small though, with a maximum difference between the two versions of 2.83\%.
\CP{Quelle figure? est ce \ref{fig:weak3} pour de petit nombre de core? Si oui, \`a mod\'erer car MSF devient meilleur quand le nombre de core augmente}

The only noticeable difference between the two versions are due to \llc which load dynamic libraries at runtime. Because of this particularity, components of \llc are compiled with the \emph{-fpic} compilation flag\footnote{\llc has been recently extended with the possibility of static linking.} while the SkelGIS version does not. This flag can have slight positive or negative effect on code performance depending on the situation and might be responsible for the observed difference.

@@

Figure~\ref{fig:strong} shows the number of iteration per second for a 10k$\times$10k global domain size from 16 to 16,384 cores. The total number of time iterations for this benchmark is $1000$. In addition to the reference SkelGIS version, the ideal strong scaling is also plotted in the figure.

First, one can notice that the strong scaling evaluated for the MSF version is close to the ideal speedup up to 16,384 cores, which is a very good result. Moreover, no overheads are introduced by MSF which shows that automatic synchronizations and automatic fusions enable the same level of performance than the one manually written into the plain SkelGIS version. Finally, no overheads are introduced by components of \llc. A small behavior difference can be noticed with $2^9=512$ cores, however this variation is no longer observed with 1024 cores.
\CP{Un commentaire sur le d\'ecrochage par rapport au perfect speedup pour $2^9--2^{12}$??}

@@

In this section, we add task parallelism to evaluate the hybrid parallelization offered by MSF. The MSF implementation evaluated in this paper relies on SkelGIS and OpenMP.

@@

\begin{figure}[th]\begin{center}
  \includegraphics[width=.6\textwidth]{../results/task_scaling/500_200/analytic/times.pdf}
  \caption{Computation vs communication times in the data parallelization technique.}
  \label{fig:limit}
  \CP{es tu sûr que le temps soit en puissance de 2 et pas en puissance de 10? C'est strange.}
\end{center}\end{figure}

On the other hand, Figure~\ref{fig:limit} illustrates limitations of data parallelization technique alone. This figure displays the execution time (with a logarithmic scale) of FullSWOF2D while increasing the number of cores for a fix domain size of $500 \times 500$ with a total of $200$ time iterations (\ie this is a strong scaling). The speedup of this same benchmark is represented in blue in Figure~\ref{fig:close}. One can note that the scaling is not as good as the one presented in Figure~\ref{fig:strong}. 
The main difference between these two benchmarks is the domain size. In the benchmark of Figure~\ref{fig:strong} the domain size is $10k \times 10k$ which means that using $2^8 = 256$ cores, for example, each core has to compute only a $31 \times 31$ sub-domain. On the other hand using $2^8$ cores in Figure~\ref{fig:close} each core has to compute a $625 \times 625$ sub-domain. Figure~\ref{fig:limit} shows why the speedup is not as good as the one with a bigger domain size.

@@

All in all, when the number of used core increases, the computation/communication ratio becomes poorer and poorer. As a result, the data parallelism alone fails to provide enough parallelism to leverage the whole machine and other sources of parallelism have to be found. As expected, in  Figure~\ref{fig:close} the speedup bends down from 256 to 2048 cores. The same problem would happened in previous experiment of Figure~\ref{fig:strong}, however as the domain size is larger, the phenomena appears with more cores.

@@

In addition to the blue curve, Figure~\ref{fig:close} shows speedups for the same example ($500 \times 500$ domain with $200$ iterations) but using an hybrid parallelization. Figure~\ref{fig:close} shows a comparison with 2, 4, 8 and 16 cores per MPI process for task parallelization.

For example, the purple curve shows the parallelization which uses for each data parallelization process (\ie MPI process) 8 additional cores for task parallelization. As a result, for example, when using 2 machines of the TGCC cluster, with a total of 32 cores, 4 cores are used for SkelGIS MPI processes, for data parallelization, and for each one 8 cores are used for task parallelization ($4 \times 8 = 32$). This respects $P = P_{data} \times P_{task}$ as presented in Section~\ref{sect:perfs}.
As a result, and as explained in Section~\ref{sect:perfs}, quantities that are responsible for communications are less divided into sub-domains. Therefore, the effect observed with the blue curve is delayed to a higher number of cores.

@@

First, thin nodes of the TGCC Curie are built with two NUMA socket each of 8 cores. As a result, when increasing the number of OpenMP cores for task parallelization from 8 to 16 cores, an overhead is introduced by exchanges of data between memories of the two NUMA sockets. This phenomena is illustrated in Figure~\ref{fig:spread}. In this figure, a different binding strategy is used. A binding strategy is the way the scheduler binds threads onto available cores. The strategy used in Figure~\ref{fig:spread} is called \emph{spread} (instead of \emph{close} in Figure~\ref{fig:close}). This strategy binds threads on cores in order to spread as much as possible onto resources, which means that the two NUMA sockets are used whatever the number of cores used for task parallelism. As a result, and as shown in the figure, using 2, 4 and 8 cores an initial overhead is introduced as the one observed in Figure~\ref{fig:close}. This shows that the initial overhead with 16 cores is due to NUMA effects.

@@

The second phenomena that happens in Figure~\ref{fig:close} using 16 cores is due to the level of parallelism introduced by the task parallelization technique. Actually, as illustrated in Table~\ref{fig:freq}, only two forks of $TSP$ can take advantage of 16 cores among a total of 18 forks. This phenomena has been mentioned in Section~\ref{sect:perfs} by the variable $F_{task}$ and the fact that it is not always true that $F_{task}=P_{task}$. This explains why using 16 cores is less efficient than using 8 cores, even when the two NUMA sockets are always used as in Figure~\ref{fig:spread}.

Finally, to validate the performance model introduced in Section~\ref{sect:perfs}, and to understand when the hybrid parallelization becomes more interesting than the data parallelization, Figure~\ref{fig:tth2} represents $T_{COM1}$ and $T_{COM2}+T_{task}$ of Equation~(\ref{eq:hyb}), for the best case, \ie when 8 cores are used in Figure~\ref{fig:close}.  Figure~\ref{fig:tth2} and Table~\ref{fig:tth} presents results of these measurements. Results perfectly matches Figure~\ref{fig:close} for 8 cores per MPI process. As a result, the hybrid parallelization is better for 512 cores or more in this case.

@@

\begin{figure}[!h]\begin{center}
  \resizebox{8cm}{!}{\includegraphics{../results/task_scaling/500_200/analytic/tth.pdf}}
  \caption{Execution times (seconds) of $T_{COM1}$ and $T_{COM2} + T_{task}$ for 8 cores for task parallelization. Verification of the Equation~(\ref{eq:hyb}).}
  \label{fig:tth2}
\CP{Time en puissance de 2 ou de 10 ?}
\end{center}\end{figure}

@@

In this section we propose an evaluation of the fusion optimization. Three fusion optimizations
\CP{les rappeler !}
%
have been formally detailed in Section~\ref{sect:fusion}. From the $TSP$ tree computed by MSC it is possible according to specific conditions to merge domain loops of kernels, thus optimizing the use of cache memories.

Figure~\ref{fig:fusion} shows the number of iterations per second as a function of the number of cores with and without fusions. This benchmark is performed on FullSWOF2D onto a $500 \times 500$ domain size with $200$ time iterations, and by using data parallelism alone (without tasks). As explained in Section~\ref{sect:fusion}, the MSF loop fusion happens at a high level. Most of the time such fusions are done naturally by a computer scientist. However, for a numerician who usually writes equations more than numerical codes, an automatic detection of such fusions avoids errors, particularly for a parallel execution. In addition to this, more advanced fusion cases, such as a scatter are more difficult to deduce. In FullSWOF2D a total of  62 fusions are proposed by MSF over a total of 98 computation kernels. Figure~\ref{fig:fusion} shows that the performance is clearly improved (around 40\%) by these fusions.

@@

Blue curves of Figure~\ref{fig:fusion1} represent results for data parallelism only with and without fusion. One can note that the best performance, as expected, is reached by the version using fusions. Green curves represent results by using 2 cores per MPI process dedicated for tasks, with and without fusion again. One can note that the best performance is also reached by the version using fusion.
\CP{PARAGRAPHE A ADAPTER SUIVANT LES MODIFS DE LA FIGURE: 1 ou 2 exp dans la figure?}

\begin{figure}[!h]\begin{center}
  \includegraphics[width=.6\textwidth]{../results/task_scaling/500_200/withwithout2_close_median.pdf}
  \caption{blabla}
  \label{fig:fusion1}
  \CP{A FINIR !!! ERREUR DANS LEGENDES AUSSI. COULEUR PROCHES}
\end{center}\end{figure}

However, to deeper analyze this results, we propose a second evaluation presented in Figure~\ref{fig:fusion2}. The blue curves are exactly the same one than in Figure~\ref{fig:fusion1}. The purple \CP{Couleur trop subtil: peux tu prendre une autre couleur, par ex rouge} curves, on the other hand, represent results by using 8 cores per MPI process dedicated to tasks, with and without fusion. Interesting results appears in this figure as the hybrid version using fusions is less efficient than the one without fusions. As already explained, this result is due to the fact that fusions reduce the number of tasks from 98 to 36 resulting in a non optimized use of eight cores for task parallelism. By using only 2 cores per MPI process (in Figure~\ref{fig:fusion1}) the 36 computation kernels were enough to feed the two cores, while it is not for eight.

\begin{figure}[!h]\begin{center}
  \includegraphics[width=.6\textwidth]{../results/task_scaling/500_200/withwithout8_close_median.pdf}
  \caption{blabla}
  \label{fig:fusion2}
    \CP{A FINIR !!! ERREUR DANS LEGENDES AUSSI.}
\end{center}\end{figure}

As a result, if fusion optimization incurs a too large reduction of the number of tasks to feed dedicated cores, the problem observed for 16 cores in Figure~\ref{fig:close} happens earlier which reduces obtained performances.
